Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Adding info on library calls in shinyapps.io version.

As the dashboard uses a fair number of packages, it uses the pacman package to ensure they are installed, to avoid the user being confronted with (cryptic) messages about missing functions:

>>>>

As the dashboard uses a fair number of packages, it uses the pacman package to ensure they are installed, to avoid the user being confronted with (cryptic) messages about missing functions when running the dashboard locally:^[A test version uploaded to [shinyapps.io](https://www.shinyapps.io) uses normal serial library calls, as the server then automatically installs the necessary packages during deployment.]
